\mutagen: Coverage-Guided, Property-Based Testing using Exhaustive Type-Preserving Mutations

### 2021-04-16 papers/oopsla-21/main.tex
NIT

Being exhaustive, these approaches rely on pruning mechanisms to avoid
populating unevaluated subexpresions exhaustively before the computational cost
becomes too restrictive.
%
\emph{LazySmallCheck} is a variant of \emph{SmallCheck} that uses lazy
evaluation to automatically prune the search space by detecting unevaluated
subexpressions using lazy evaluation.
%
In the case of \emph{Korat}, pruning is done by instrumenting method
precondition predicates and analyzing which parts of the execution trace
correspond to each evaluated subexpression.

>>>>

Being exhaustive, these approaches rely on pruning mechanisms to avoid
populating unevaluated subexpresions exhaustively before the computational cost
becomes too restrictive.
%
\emph{LazySmallCheck} is a variant of \emph{SmallCheck} that uses lazy
evaluation to automatically prune the search space by detecting unevaluated
subexpressions.
%
In the case of \emph{Korat}, pruning is done by instrumenting method
precondition predicates and analyzing which parts of the execution trace
correspond to each evaluated subexpression.
